Supplementary material

### 2025-07-15 code/supplementary.Rmd
updaded review for manuscript and updated readme file

```{r meanerr, fig.cap="Distribution of estimated deviation from the ground-truth savings calculated by the two M&V methods (red dashed line highlighting 0% error)", fig.height=7, fig.width=9}
# plot for the stable subset
rand_eob_S <- df_seq_fs_stable %>% 
  filter(seq == "eob") %>% 
  left_join(df_fs_stable %>% filter(scenario == "ref" & method == "true"), by = c("name", "site")) %>% 
  mutate(diff = savings - fs, 
         method = "rand_eob") %>% 
  select(name, method, diff)

@@

p_top <- df_MW_A %>% 
  mutate(method = as.factor(method), 
         method = recode_factor(method, "conv_diff" = "Conventional", "rand_eob_diff" = "Randomized", "rand_final_diff" = "Randomized\n(24 months)")) %>% 
  ggplot(aes(x = method, y = diff, fill = method)) +
  geom_lv(k = 4, outlier.shape = NA) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = method), linewidth = 0.25) +
  geom_hline(yintercept = 0, color = "#fb8072", linewidth = 1.5, lty = "dashed") +
  geom_text(data = . %>% group_by(method) %>% summarise(median = median(diff)) %>% ungroup(), 
            aes(x = method, y = median, label = paste0(round(median, digits = 1), " %")), 
            size = 5) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 5), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80", "grey80")) + 
  labs(fill = NULL, 
       color = NULL, 
       x = NULL, 
       y = "Estimated error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with measured weather")) +
  coord_cartesian(ylim = c(-15, 15)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "none",
        axis.text.x = element_blank(),
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

@@

p_middle <- df_TW_A %>% 
  mutate(method = as.factor(method), 
         method = recode_factor(method, "conv_diff" = "Conventional", "rand_eob_diff" = "Randomized", "rand_final_diff" = "Randomized\n(24 months)")) %>% 
  ggplot(aes(x = method, y = diff, fill = method)) +
  geom_lv(k = 4, outlier.shape = NA) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = method), linewidth = 0.25) +
  geom_hline(yintercept = 0, color = "#fb8072", linewidth = 1.5, lty = "dashed") +
  geom_text(data = . %>% group_by(method) %>% summarise(median = median(diff)) %>% ungroup(), 
            aes(x = method, y = median, label = paste0(round(median, digits = 1), " %")), 
            size = 5) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 5), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80", "grey80")) + 
  labs(fill = NULL, 
       x = NULL, 
       y = "Estimated error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with TOWT model and TMY weather")) +
  coord_cartesian(ylim = c(-15, 15)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "none",
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

ggarrange(p_top, p_middle, 
          ncol = 1, nrow = 2,
          labels = c("a)", "b)")) +
  plot_annotation(title = "Estimated error in savings estimation by different M&V methods")

@@

```{r absnull, fig.cap="Comparison between the two M&V methods in detecting no intervention effect (expressed without absolute calculation) when buildings are subject to baseline change.", fig.height=4, fig.width=9}
#### ABS-NULL ####
rand_eob_S <- df_seq_fs_null_stable %>% 
  filter(seq == "eob") %>% 
  mutate(diff = abs(0 - fs), 
         method = "rand_eob") %>% 
  select(name, method, diff)

@@

```{r meancont, fig.cap="Comparison of different sampling ratio impact on M&V estimation accuracy (expressed without absolute calculation for errors)", fig.height=7, fig.width=9}

p_top <- df_MW_A %>% 
  mutate(ratio = as.factor(ratio), 
         ratio = recode_factor(ratio, 
                               "0" = "Randomized\n(50/50)", 
                               "1_1" = "Continued\n(20/80)", 
                               "1_2" = "Randomized\n(20/80)", 
                               "2_1" = "Continued\n(10/90)", 
                               "2_2" = "Randomized\n(10/90)")) %>% 
  ggplot(aes(x = ratio, y = values, fill = ratio)) +
  geom_lv(k = 4, outlier.shape = NA, position = position_jitterdodge(dodge.width = 0.75, jitter.width = 0.1)) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = ratio), width = 0.75, linewidth = 0.15) +
  geom_vline(xintercept = 1.5, color = "#fb8072", linewidth = 1, lty = "dashed") +
  geom_text(data = . %>% 
              group_by(ratio) %>% 
              summarise(median = median(values)) %>% 
              ungroup(), 
            aes(x = ratio, y = median, label = paste0(round(median, digits = 1), " %")), 
            size = 5) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 5), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80", "grey80", "grey80", "grey80")) + 
  labs(fill = NULL, 
       x = NULL, 
       y = "Absolute error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with measured weather conditions")) +
  coord_cartesian(ylim = c(-12, 15)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "none",
        axis.text.x = element_blank(), 
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

p_bottom <- df_TW_A %>% 
  mutate(ratio = as.factor(ratio), 
         ratio = recode_factor(ratio, 
                               "0" = "Randomized\n(50/50)", 
                               "1_1" = "Continued\n(20/80)", 
                               "1_2" = "Randomized\n(20/80)", 
                               "2_1" = "Continued\n(10/90)", 
                               "2_2" = "Randomized\n(10/90)")) %>% 
  ggplot(aes(x = ratio, y = values, fill = ratio)) +
  geom_lv(k = 4, outlier.shape = NA, position = position_jitterdodge(dodge.width = 0.75, jitter.width = 0.1)) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = ratio), width = 0.75, linewidth = 0.15) +
  geom_vline(xintercept = 1.5, color = "#fb8072", linewidth = 1, lty = "dashed") +
  geom_text(data = . %>% 
              group_by(ratio) %>% 
              summarise(median = median(values)) %>% 
              ungroup(), 
            aes(x = ratio, y = median, label = paste0(round(median, digits = 1), " %")), 
            size = 5) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 5), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80", "grey80", "grey80", "grey80")) + 
  labs(fill = NULL, 
       x = NULL, 
       y = "Absolute error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with TOWT model and TMY weather")) +
  coord_cartesian(ylim = c(-12, 15)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "none",
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

ggarrange(p_top, p_bottom, 
          ncol = 1, nrow = 2,
          labels = c("a)", "b)")) +
  plot_annotation(title = "Absolute error in savings estimation by different sampling ratio")
```

@@

@@

ggarrange(p_top, p_bottom, 
          ncol = 1, nrow = 2,
          labels = c("a)", "b)")) +
  plot_annotation(title = "Absolute error in savings estimation by different sampling ratio")
```

@@

ggarrange(p_top, p_bottom, 
          ncol = 1, nrow = 2, 
          align = "hv", 
          labels = c("a)", "b)"),
          common.legend = T, 
          legend = "bottom") +
  plot_annotation(title = "Absolute error in savings estimation of ranodmized M&V\nafter 2 years")
```

@@

p_top <- df_MW_A %>% 
  mutate(interval = as.factor(interval), 
         interval = recode_factor(interval, 
                                  "1" = "1-day\nsampling",
                                  "2" = "2-day\nsampling", 
                                  "3" = "3-day\nsampling", 
                                  "7" = "7-day\nsampling"), 
         group = as.factor(group), 
         group = recode_factor(group, "drop" = "Dropped", "keep" = "Kept")) %>% 
  ggplot(aes(x = interval, y = diff, fill = group)) +
  geom_lv(k = 4, outlier.shape = NA, position = position_dodge(width = 0.8)) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = group), width = 0.8, linewidth = 0.15) +
  geom_hline(yintercept = 0, color = "#fb8072", linewidth = 1, lty = "dashed") +
  geom_text(data = . %>% group_by(group, interval) %>% summarise(median = median(diff, inf.rm = T)) %>% ungroup(), 
            aes(x = interval, y = median, group = group,
                label = paste0(round(median, digits = 1), " %")), 
            position = position_dodge(width = 0.75), 
            size = 5, 
            color = "white") +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 5), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80")) + 
  labs(fill = NULL, 
       color = NULL, 
       x = NULL, 
       y = "Estimated error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with measured weather")) +
  coord_cartesian(ylim = c(-10, 10)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "bottom",
        axis.text.x = element_blank(),
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

@@

p_bottom <- df_TW_A %>% 
  mutate(interval = as.factor(interval), 
         interval = recode_factor(interval, 
                                  "1" = "1-day\nsampling",
                                  "2" = "2-day\nsampling", 
                                  "3" = "3-day\nsampling", 
                                  "7" = "7-day\nsampling"), 
         group = as.factor(group), 
         group = recode_factor(group, "drop" = "Dropped", "keep" = "Kept")) %>% 
  ggplot(aes(x = interval, y = diff, fill = group)) +
  geom_lv(k = 4, outlier.shape = NA, position = position_dodge(width = 0.8)) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = group), width = 0.8, linewidth = 0.15) +
  geom_hline(yintercept = 0, color = "#fb8072", linewidth = 1, lty = "dashed") +
  geom_text(data = . %>% group_by(group, interval) %>% summarise(median = median(diff, na.rm = T)) %>% ungroup(), 
            aes(x = interval, y = median, group = group,
                label = paste0(round(median, digits = 1), " %")), 
            position = position_dodge(width = 0.75), 
            size = 5, 
            color = "white") +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 5), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80")) + 
  labs(fill = NULL, 
       color = NULL, 
       x = NULL, 
       y = "Esimated error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with TOWT model and TMY weather")) +
  coord_cartesian(ylim = c(-10, 10)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "bottom",
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

ggarrange(p_top, p_bottom, 
          ncol = 1, nrow = 2, 
          align = "hv", 
          labels = c("a)", "b)"),
          common.legend = T, 
          legend = "bottom") +
  plot_annotation(title = "Estimated error in savings estimation of randomized M&V\nafter satisfying all stopping criteria")

@@

p_top <- df_MW_A %>% 
  mutate(interval = as.factor(interval), 
         interval = recode_factor(interval, 
                                  "1" = "1-day\nsampling",
                                  "2" = "2-day\nsampling", 
                                  "3" = "3-day\nsampling", 
                                  "7" = "7-day\nsampling"), 
         group = as.factor(group), 
         group = recode_factor(group, "drop" = "Dropped", "keep" = "Kept")) %>% 
  ggplot(aes(x = interval, y = diff, fill = group)) +
  geom_lv(k = 4, outlier.shape = NA, position = position_dodge(width = 0.8)) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = group), width = 0.8, linewidth = 0.15) +
  geom_hline(yintercept = 0, color = "#fb8072", linewidth = 1, lty = "dashed") +
  geom_text(data = . %>% group_by(group, interval) %>% summarise(median = median(diff, na.rm = T)) %>% ungroup(), 
            aes(x = interval, y = median, group = group,
                label = paste0(round(median, digits = 1), " %")), 
            position = position_dodge(width = 0.75), 
            size = 5, 
            color = "white") +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 5), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80")) + 
  labs(fill = NULL, 
       color = NULL, 
       x = NULL, 
       y = "Estimated error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with measured weather")) +
  coord_cartesian(ylim = c(-5, 5)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "bottom",
        axis.text.x = element_blank(),
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

>>>>

```{r meanerr, fig.cap="Distribution of estimated deviation (without absolute calculation) from the ground-truth savings calculated by the two M&V methods (red dashed line highlighting 0% error)", fig.height=7, fig.width=9}
# plot for the stable subset
rand_eob_S <- df_seq_fs_stable %>% 
  filter(seq == "eob") %>% 
  left_join(df_fs_stable %>% filter(scenario == "ref" & method == "true"), by = c("name", "site")) %>% 
  mutate(diff = savings - fs, 
         method = "rand_eob") %>% 
  select(name, method, diff)

@@

p_top <- df_MW_A %>% 
  mutate(method = as.factor(method), 
         method = recode_factor(method, "conv_diff" = "Conventional", "rand_eob_diff" = "Randomized", "rand_final_diff" = "Randomized\n(24 months)")) %>% 
  ggplot(aes(x = method, y = diff, fill = method)) +
  geom_lv(k = 4, outlier.shape = NA) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = method), linewidth = 0.25) +
  geom_hline(yintercept = 0, color = "#fb8072", linewidth = 1.5, lty = "dashed") +
  geom_text(data = . %>% group_by(method) %>% summarise(median = median(diff)) %>% ungroup(), 
            aes(x = method, y = median, label = paste0(round(median, digits = 1), " %")), 
            size = 5) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 5), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80", "grey80")) + 
  labs(fill = NULL, 
       color = NULL, 
       x = NULL, 
       y = "Signed error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with measured weather")) +
  coord_cartesian(ylim = c(-15, 15)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "none",
        axis.text.x = element_blank(),
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

@@

p_middle <- df_TW_A %>% 
  mutate(method = as.factor(method), 
         method = recode_factor(method, "conv_diff" = "Conventional", "rand_eob_diff" = "Randomized", "rand_final_diff" = "Randomized\n(24 months)")) %>% 
  ggplot(aes(x = method, y = diff, fill = method)) +
  geom_lv(k = 4, outlier.shape = NA) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = method), linewidth = 0.25) +
  geom_hline(yintercept = 0, color = "#fb8072", linewidth = 1.5, lty = "dashed") +
  geom_text(data = . %>% group_by(method) %>% summarise(median = median(diff)) %>% ungroup(), 
            aes(x = method, y = median, label = paste0(round(median, digits = 1), " %")), 
            size = 5) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 5), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80", "grey80")) + 
  labs(fill = NULL, 
       x = NULL, 
       y = "Signed error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with TOWT model and TMY weather")) +
  coord_cartesian(ylim = c(-15, 15)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "none",
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

ggarrange(p_top, p_middle, 
          ncol = 1, nrow = 2,
          labels = c("a)", "b)")) +
  plot_annotation(title = "Signed error in savings estimation by different M&V methods")

@@

```{r absnull, fig.cap="Comparison between the two M&V methods in detecting no intervention effect when buildings are subject to baseline change.", fig.height=4, fig.width=9}
#### ABS-NULL ####
rand_eob_S <- df_seq_fs_null_stable %>% 
  filter(seq == "eob") %>% 
  mutate(diff = abs(0 - fs), 
         method = "rand_eob") %>% 
  select(name, method, diff)

@@

@@

df_MW_S <- df_cont_stable %>% 
  left_join(df_fs_stable %>% filter(scenario == "ref" & method == "true"), by = c("name", "site")) %>% 
  mutate(diff = abs(savings - cont_fs), 
         diff_all = abs(savings - cont_fs_all)) %>% 
  select(name, diff, diff_all, ratio) %>% 
  pivot_longer(c(diff, diff_all), names_to = "type", values_to = "values") %>% 
  mutate(ratio = ifelse(ratio == 1 & type == "diff", "1_1", 
                        ifelse(ratio == 1 & type == "diff_all", "1_2", 
                               ifelse(ratio == 2 & type == "diff", "2_1", 
                                      ifelse(ratio == 2 & type == "diff_all", "2_2", ratio))))) %>% 
  bind_rows(df_fs_stable %>% 
              filter(method != "conv") %>% 
              pivot_wider(names_from = method, values_from = savings) %>% 
              mutate(values = abs(true - rand), 
                     ratio = "0", 
                     type = "diff_ref") %>% 
              select(name, values, ratio, type))

@@

ggarrange(p_top, p_bottom, 
          ncol = 1, nrow = 2,
          labels = c("a)", "b)")) +
  plot_annotation(title = "Absolute error in savings estimation by different sampling ratio\n(after 2 years)")
```

```{r stablecont, fig.cap="Comparison of different sampling ratio impact on M&V estimation accuracy using buildings with stable electricity usage over the entire 24 months (results of sampling at 50%/50% shown on the left side of the red dashed line)", fig.height=7, fig.width=9}

p_top <- df_MW_S %>% 
  mutate(ratio = as.factor(ratio), 
         ratio = recode_factor(ratio, 
                               "0" = "Randomized\n(50/50)", 
                               "1_1" = "Continued\n(20/80)", 
                               "1_2" = "Randomized\n(20/80)", 
                               "2_1" = "Continued\n(10/90)", 
                               "2_2" = "Randomized\n(10/90)")) %>% 
  ggplot(aes(x = ratio, y = values, fill = ratio)) +
  geom_lv(k = 4, outlier.shape = NA, position = position_jitterdodge(dodge.width = 0.75, jitter.width = 0.1)) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = ratio), width = 0.75) +
  geom_vline(xintercept = 1.5, color = "#fb8072", linewidth = 1, lty = "dashed") +
  geom_text(data = . %>% 
              group_by(ratio) %>% 
              summarise(median = median(values)) %>% 
              ungroup(), 
            aes(x = ratio, y = median, label = paste0(round(median, digits = 1), " %")), 
            size = 5) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 4), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80", "grey80", "grey80", "grey80")) + 
  labs(fill = NULL, 
       x = NULL, 
       y = "Absolute error in fractional savings", 
       subtitle = str_glue("{S_building} buildings in the stable subset with measured weather conditions")) +
  coord_cartesian(ylim = c(0, 8)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "none",
        axis.text.x = element_blank(), 
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

p_bottom <- df_TW_S %>% 
  mutate(ratio = as.factor(ratio), 
         ratio = recode_factor(ratio, 
                               "0" = "Randomized\n(50/50)", 
                               "1_1" = "Continued\n(20/80)", 
                               "1_2" = "Randomized\n(20/80)", 
                               "2_1" = "Continued\n(10/90)", 
                               "2_2" = "Randomized\n(10/90)")) %>% 
  ggplot(aes(x = ratio, y = values, fill = ratio)) +
  geom_lv(k = 4, outlier.shape = NA, position = position_jitterdodge(dodge.width = 0.75, jitter.width = 0.1)) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = ratio), width = 0.75) +
  geom_vline(xintercept = 1.5, color = "#fb8072", linewidth = 1, lty = "dashed") +
  geom_text(data = . %>% 
              group_by(ratio) %>% 
              summarise(median = median(values)) %>% 
              ungroup(), 
            aes(x = ratio, y = median, label = paste0(round(median, digits = 1), " %")), 
            size = 5) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 4), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80", "grey80", "grey80", "grey80")) + 
  labs(fill = NULL, 
       x = NULL, 
       y = "Absolute error in fractional savings", 
       subtitle = str_glue("{S_building} buildings in the stable subset with TOWT model and TMY weather")) +
  coord_cartesian(ylim = c(0, 8)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "none",
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

ggarrange(p_top, p_bottom, 
          ncol = 1, nrow = 2,
          labels = c("a)", "b)")) +
  plot_annotation(title = "Absolute error in savings estimation by different sampling ration(after 2 years)")
```

```{r meancont, fig.cap="Comparison of different sampling ratio impact on M&V estimation accuracy at the time of satisfying all stopping criteria (expressed without absolute calculation for errors)", fig.height=7, fig.width=9}

p_top <- df_MW_A %>% 
  mutate(ratio = as.factor(ratio), 
         ratio = recode_factor(ratio, 
                               "0" = "Randomized\n(50/50)", 
                               "1_1" = "Continued\n(20/80)", 
                               "1_2" = "Randomized\n(20/80)", 
                               "2_1" = "Continued\n(10/90)", 
                               "2_2" = "Randomized\n(10/90)")) %>% 
  ggplot(aes(x = ratio, y = values, fill = ratio)) +
  geom_lv(k = 4, outlier.shape = NA, position = position_jitterdodge(dodge.width = 0.75, jitter.width = 0.1)) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = ratio), width = 0.75, linewidth = 0.15) +
  geom_vline(xintercept = 1.5, color = "#fb8072", linewidth = 1, lty = "dashed") +
  geom_text(data = . %>% 
              group_by(ratio) %>% 
              summarise(median = median(values)) %>% 
              ungroup(), 
            aes(x = ratio, y = median, label = paste0(round(median, digits = 1), " %")), 
            size = 5) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 5), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80", "grey80", "grey80", "grey80")) + 
  labs(fill = NULL, 
       x = NULL, 
       y = "Signed error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with measured weather conditions")) +
  coord_cartesian(ylim = c(-12, 15)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "none",
        axis.text.x = element_blank(), 
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

p_bottom <- df_TW_A %>% 
  mutate(ratio = as.factor(ratio), 
         ratio = recode_factor(ratio, 
                               "0" = "Randomized\n(50/50)", 
                               "1_1" = "Continued\n(20/80)", 
                               "1_2" = "Randomized\n(20/80)", 
                               "2_1" = "Continued\n(10/90)", 
                               "2_2" = "Randomized\n(10/90)")) %>% 
  ggplot(aes(x = ratio, y = values, fill = ratio)) +
  geom_lv(k = 4, outlier.shape = NA, position = position_jitterdodge(dodge.width = 0.75, jitter.width = 0.1)) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = ratio), width = 0.75, linewidth = 0.15) +
  geom_vline(xintercept = 1.5, color = "#fb8072", linewidth = 1, lty = "dashed") +
  geom_text(data = . %>% 
              group_by(ratio) %>% 
              summarise(median = median(values)) %>% 
              ungroup(), 
            aes(x = ratio, y = median, label = paste0(round(median, digits = 1), " %")), 
            size = 5) +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 5), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80", "grey80", "grey80", "grey80")) + 
  labs(fill = NULL, 
       x = NULL, 
       y = "Signed error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with TOWT model and TMY weather")) +
  coord_cartesian(ylim = c(-12, 15)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "none",
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

ggarrange(p_top, p_bottom, 
          ncol = 1, nrow = 2,
          labels = c("a)", "b)")) +
  plot_annotation(title = "Absolute error in savings estimation by different sampling ration\n(after satisfying all stopping criteria)")
```

@@

ggarrange(p_top, p_bottom, 
          ncol = 1, nrow = 2, 
          align = "hv", 
          labels = c("a)", "b)"),
          common.legend = T, 
          legend = "bottom") +
  plot_annotation(title = "Absolute error in savings estimation of ranodmized M&V\n(after 2 years)")
```

@@

p_top <- df_MW_A %>% 
  mutate(interval = as.factor(interval), 
         interval = recode_factor(interval, 
                                  "1" = "1-day\nsampling",
                                  "2" = "2-day\nsampling", 
                                  "3" = "3-day\nsampling", 
                                  "7" = "7-day\nsampling"), 
         group = as.factor(group), 
         group = recode_factor(group, "drop" = "Dropped", "keep" = "Kept")) %>% 
  ggplot(aes(x = interval, y = diff, fill = group)) +
  geom_lv(k = 4, outlier.shape = NA, position = position_dodge(width = 0.8)) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = group), width = 0.8, linewidth = 0.15) +
  geom_hline(yintercept = 0, color = "#fb8072", linewidth = 1, lty = "dashed") +
  geom_text(data = . %>% group_by(group, interval) %>% summarise(median = median(diff, inf.rm = T)) %>% ungroup(), 
            aes(x = interval, y = median, group = group,
                label = paste0(round(median, digits = 1), " %")), 
            position = position_dodge(width = 0.75), 
            size = 5, 
            color = "white") +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 5), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80")) + 
  labs(fill = NULL, 
       color = NULL, 
       x = NULL, 
       y = "Signed error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with measured weather")) +
  coord_cartesian(ylim = c(-10, 10)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "bottom",
        axis.text.x = element_blank(),
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

@@

p_bottom <- df_TW_A %>% 
  mutate(interval = as.factor(interval), 
         interval = recode_factor(interval, 
                                  "1" = "1-day\nsampling",
                                  "2" = "2-day\nsampling", 
                                  "3" = "3-day\nsampling", 
                                  "7" = "7-day\nsampling"), 
         group = as.factor(group), 
         group = recode_factor(group, "drop" = "Dropped", "keep" = "Kept")) %>% 
  ggplot(aes(x = interval, y = diff, fill = group)) +
  geom_lv(k = 4, outlier.shape = NA, position = position_dodge(width = 0.8)) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = group), width = 0.8, linewidth = 0.15) +
  geom_hline(yintercept = 0, color = "#fb8072", linewidth = 1, lty = "dashed") +
  geom_text(data = . %>% group_by(group, interval) %>% summarise(median = median(diff, na.rm = T)) %>% ungroup(), 
            aes(x = interval, y = median, group = group,
                label = paste0(round(median, digits = 1), " %")), 
            position = position_dodge(width = 0.75), 
            size = 5, 
            color = "white") +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 5), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80")) + 
  labs(fill = NULL, 
       color = NULL, 
       x = NULL, 
       y = "Signed error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with TOWT model and TMY weather")) +
  coord_cartesian(ylim = c(-10, 10)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "bottom",
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))

ggarrange(p_top, p_bottom, 
          ncol = 1, nrow = 2, 
          align = "hv", 
          labels = c("a)", "b)"),
          common.legend = T, 
          legend = "bottom") +
  plot_annotation(title = "Signed error in savings estimation of randomized M&V\n(after satisfying all stopping criteria)")

@@

p_top <- df_MW_A %>% 
  mutate(interval = as.factor(interval), 
         interval = recode_factor(interval, 
                                  "1" = "1-day\nsampling",
                                  "2" = "2-day\nsampling", 
                                  "3" = "3-day\nsampling", 
                                  "7" = "7-day\nsampling"), 
         group = as.factor(group), 
         group = recode_factor(group, "drop" = "Dropped", "keep" = "Kept")) %>% 
  ggplot(aes(x = interval, y = diff, fill = group)) +
  geom_lv(k = 4, outlier.shape = NA, position = position_dodge(width = 0.8)) +
  geom_boxplot(outlier.alpha = 0, coef = 0, fill = "#00000000", aes(color = group), width = 0.8, linewidth = 0.15) +
  geom_hline(yintercept = 0, color = "#fb8072", linewidth = 1, lty = "dashed") +
  geom_text(data = . %>% group_by(group, interval) %>% summarise(median = median(diff, na.rm = T)) %>% ungroup(), 
            aes(x = interval, y = median, group = group,
                label = paste0(round(median, digits = 1), " %")), 
            position = position_dodge(width = 0.75), 
            size = 5, 
            color = "white") +
  scale_y_continuous(expand = c(0, 0), 
                     breaks = breaks_pretty(n = 5), 
                     labels = number_format(suffix = " %")) +
  scale_fill_manual(values = ls_colors) +
  scale_color_manual(values = c("grey80", "grey80")) + 
  labs(fill = NULL, 
       color = NULL, 
       x = NULL, 
       y = "Signed error in fractional savings", 
       subtitle = str_glue("All {A_building} buildings with measured weather")) +
  coord_cartesian(ylim = c(-5, 5)) +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        legend.position = "bottom",
        axis.text.x = element_blank(),
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))
